\Rpackage{MSnbase}: labelled MS2 data pre-processing, visualisation and quantification.

### 2012-07-15 inst/doc/MSnbase-demo/MSnbase-demo.Rnw
typos in filterNA and demo vignette
git-svn-id: https://hedgehog.fhcrc.org/bioconductor/trunk/madman/Rpacks/MSnbase@67664 bc3139a8-67e5-0310-9ffc-ced21a209358

\paragraph{Experiments with multiple runs} Although it is possible to load and process multiple 
files serially and later merge the resulting quantitation data as show in section 
\ref{sec:combine} (page \pageref{sec:combine}), it is also feasible to load several raw data files at once. 
Here, we report the analysis of an LC-MSMS experiment were 
14 liquid chromatography (LC) fractions were loaded using \Rfunction{readMSData} on a 
32-cores servers with 128 Gb of RAM. 
It took about 90 minutes to read the 14 uncentroided \texttt{mzXML} raw files (4.9 Gb on disk in total)
and create a 3.3 Mb raw data object (an \Robject{MSnExp} instance, see next section). 
Quantitation of 9 reporter ions (\Robject{iTRAQ9} object, see \ref{sec:reporterions}) 
for 88690 features was performed in parallel on 16 processors and took 76 minutes. 
The resulting quantitation data was only 22.1 Mb and could easily be further processed and 
analysed on a standard laptop computer.

>>>>

\paragraph{Experiments with multiple runs} Although it is possible to load and process multiple 
files serially and later merge the resulting quantitation data as show in section 
\ref{sec:combine} (page \pageref{sec:combine}), it is also feasible to load several raw data files at once. 
Here, we report the analysis of an LC-MSMS experiment were 
14 liquid chromatography (LC) fractions were loaded using \Rfunction{readMSData} on a 
32-cores servers with 128 Gb of RAM. 
It took about 90 minutes to read the 14 uncentroided \texttt{mzXML} raw files (4.9 Gb on disk in total)
and create a 3.3 Gb raw data object (an \Robject{MSnExp} instance, see next section). 
Quantitation of 9 reporter ions (\Robject{iTRAQ9} object, see \ref{sec:reporterions}) 
for 88690 features was performed in parallel on 16 processors and took 76 minutes. 
The resulting quantitation data was only 22.1 Mb and could easily be further processed and 
analysed on a standard laptop computer.
